\documentclass[10pt]{article}

\input{../preamble.tex}

\begin{document}

\makeletterhead

\vfill

\today

\vfill

Faculty Search Committee\\
c/o Search Coordinator Cindi Griffith\\
Department of Mathematics and Statistics\\
California State Polytechnic University, Pomona

\vfill

To the members of the Faculty Search Committee:

\vfill

I am contacting you today to apply for the tenure-track position in pure
Mathematics on the advice of Ivona Grzegorczyk, Chair of Mathematics at
Cal State Channel Islands and Sophia Raczkowski, Chair of Mathematics at
Cal State Bakersfield. I am currently a lecturer at Bakersfield, and
while I enjoy my teaching responsibilities, I am seeking a permanent
position that incorporates research and service responsibilities.

I earned my PhD in Linear Algebra and Lie algebras under the direction
of Huajun Huang at Auburn University in June 2014. My dissertation
research was in structure theory of Lie algebras: I found a direct sum
decomposition of the derivation algebra of an arbitrary parabolic
subalgebra of a reductive Lie algebra, which I used to show that the
derivation algebra is zero product determined. Notwithstanding my
full-time
teaching load as a Lecturer, I still find some time to maintain a
research agenda. I would very much enjoy the opportunity to further my
research efforts and to work with undergraduates and graduate students
in algebra and related fields such as computational algebra and data
analysis. As an undergraduate in the Cal State, research was a formative
experience, essential to my understanding that knowledge is not merely
something to acquire but rather something to actively
and continually strive towards.

I have been teaching university Mathematics since 2007, and my
background and interests are broad enough that, with a handful of
exceptions, I would be ready to begin teaching any course in your
undergraduate offering, including the specialized courses for preservice
teachers. I am particularly impressed by the range of specialized
courses for non-majors, such as \emph{Technical Calculus} and
\emph{Algebraic Structures for Computing and Elementary and Middle
School Teachers}, the latter I would be very interested in teaching. I
am also impressed by the presence of \emph{Topology} and
\emph{Differential Geometry} as part of the undergraduate offering. I
seldom see these in Cal State course catalogs, and I would be interested
in teaching either, as well as developing introductory courses in
Algebraic Geometry and Lie algebras. These topics, in their elementary
form, can be made accessible to senior-level Math majors and interested
Masters students. At the graduate level, I could teach any of the
algebras, analyses, and \emph{Topology}, and would enjoy researching
with interested students. While my background does not specifically
include Combinatorics or Graph Theory, I can begin teaching the
Linear-algebraic
aspects of Graph Theory, analysis of adjacency and incidence
matrices, and finite geometries and designs immediately,
confident that I can master further aspects of Discrete
Mathematics within the first years.


Thank you for the opportunity to apply to Cal Poly Pomona and for
considering my application. As a native of the Inland Valley, I
sincerely hope to join you and the rest of the faculty in Pomona this
Fall.

\vfill

Respectfully,

\vfill

Daniel Brice\\
\texttt{danielbrice@gmail.com}

\label{page:last}
\end{document}
