\documentclass[10pt]{article}

\input{../preamble.tex}

\begin{document}

\makeletterhead{}

\vfill

\today

\vfill

Department of Mathematics\\
c/o Dr. Bem Cayco\\
San Jos\'{e} State University

\vfill

To the members of the Department of Mathematics:

\vfill

I am contacting you today to apply for the position, JOID 23388,
advertised on MathJobs.org and on the advice of Dr. Ivona Grzegorczyk,
Chair of Mathematics at Cal State Channel Islands and Dr. Sophia
Raczkowski, Chair of Mathematics at Cal State Bakersfield. I am
currently a lecturer at Bakersfield, and while I enjoy my work, I am
desirous of a permanent position that incorporates research and service
responsibilities.

I earned my PhD in Linear Algebra and Lie algebras under the direction
of Dr. Huajun Huang at Auburn University in June 2014. Although it was
not required by my program, my coursework includes specialized education
courses such as \emph{Research in Mathematics Education} and
\emph{Equity Issues in Mathematics Education}, and I am committed to
using education as a means towards correcting social inequity rather
than furthering it. I have been teaching university Mathematics since
2007, and my background and interests are broad enough that I would
enjoy teaching almost your entire undergraduate course catalog,
including courses targeted at pre-service teachers and developmental
Mathematics courses. (Admittedly I would require abundant prep in order
to teach any of the numerical methods, statistics courses, or discrete
courses, but I will have no trouble teaching any of the geometry,
analysis, topology, algebra, or education courses.) Despite my position
as a Lecturer, I still find time to maintain a research agenda, mostly
in rings, non-associative algebras, and matrix theory, and would very
much enjoy the opportunity to collaborate with faculty, such as Dr. Low
and Dr. So, and to work with undergraduates in related fields such as
computational linear algebra and data analysis. As an undergraduate at
Cal State Channel Islands, my undergraduate research was a formative
experience, essential to my understanding that knowledge is not merely
something to acquire but rather something to actively and continually
strive towards.

Although I enjoy my work as a lecturer, I ultimately desire a position
that requires more contact and collaboration with my colleagues. What I
find particularly appealing about the description of JOID 23388 is the
expectation that the hired will train teaching assistants, develop and
assess curriculum, and design and implement tools that facilitate the
developmental Mathematics curriculum. I would also like to work with the
Mathematics tutors and train the Calculus Lab assistants. I enjoy the
role of mentor, and I enjoy working as a team towards a common goal. I
am also motivated by my desire to provide quality educational outcomes
to all students, as per the Social and Global Responsibilities clauses
of the San Jos\'{e} State Mission and the broader mission of the CSU
System to provide quality, accessible higher education.

\vfill

Thank you very much for your consideration. I sincerely hope to work
with you this coming August.

\vfill

Respectfully,

\vfill

Daniel Brice\\
\texttt{danielbrice@gmail.com}

\label{page:last}
\end{document}
