\documentclass[11pt]{article}

\input{../preamble.tex}

\begin{document}

\makeletterhead{}

\vfill

\today

\vfill

Department of Mathematics \& Statistics\\
c/o Dr. Thomas Mattman\\
California State University, Chico

\vfill

To the members of the Department of Mathematics \& Statistics:

\vfill

I am contacting you today to apply for the position advertised on
MathJobs.org and on the advice of Dr. Ivona Grzegorczyk, Chair of
Mathematics at Cal State Channel Islands and Dr. Sophia Raczkowski,
Chair of Mathematics at Cal State Bakersfield. I am currently a lecturer
at Bakersfield, and while I enjoy my work, I am desirous of a permanent
position that incorporates research and service responsibilities.

I earned my PhD in Linear Algebra and Lie algebras under the direction
of Dr. Huajun Huang at Auburn University in June 2014. I have been
teaching university Mathematics since 2007, and my background and
interests are broad enough that I would enjoy teaching almost your
entire course catalog, though admittedly I might need significant prep
time in order to teach \emph{Science and Strategy in War and Peace}. In
seriousness, I am able to teach any of the analyses, geometries,
topologies, and algebras on day one, and am willing to do the required
prep in order to teach the statistics and numerical analysis courses.
Despite my position as a Lecturer, I still find time to maintain a
research agenda, mostly in rings and non-associative algebras, and would
very much enjoy the opportunity to work with undergraduates in related
fields such as computational linear algebra and data analysis. As an
undergraduate at Cal State Channel Islands, my undergraduate research
was a formative experience, essential to my understanding that knowledge
is not merely something to acquire but rather something to actively and
continually strive towards.

The course offering at Chico is somewhat unique, and I am rather
impressed by it. Specifically, I refer to the specialized
interdisciplinary courses for non-majors and to the problem sessions for
the mainline calculus sequence. I am also impressed that \emph{Advanced
Calculus} features a writing prerequisite, and by the computational
requirement for Math majors (I'm already thinking about what language I
would use for such a course---I'd very much like to use Haskell, but
I'll settle for Mathematica if I must). I can see that the Math
department at Chico is very forward-thinking, placing learning outcomes
before orthodoxy, and I am excited at the prospect of becoming a member
of such a unique department.

\vfill

Respectfully,

\vfill

Daniel Brice\\
\texttt{danielbrice@gmail.com}

\label{page:last}
\end{document}
