\documentclass[11pt]{article}

\input{../preamble.tex}

\begin{document}

\makeletterhead

\vfill

\today

\vfill

Faculty Search Committee\\
c/o Ms. Leeanne Richardson\\
Department of Mathematics\\
California State University, San Bernardino

\vfill

To the members of the Faculty Search Committee:

\vfill

I am contacting you today to apply for the assistant professor position
in Mathematics on the advice of Ivona Grzegorczyk,
Chair of Mathematics at Cal State Channel Islands
and Sophia Raczkowski, Chair of Mathematics at Cal State Bakersfield.
I completed my PhD under the direction of Huajun Huang
at Auburn University in June 2014.
I am currently a lecturer at Bakersfield,
and while I enjoy my teaching responsibilities,
I am seeking a permanent position that incorporates
research and service responsibilities.

I have been teaching university Mathematics since 2007.
Since then, I have had the pleasure of working
with a diverse student body
at two Cal States (Channel Islands and Bakersfield)
and at the historic Tuskegee University.
My teaching style is informed by undergraduate and graduate coursework
in education, and by my attendance at the Mathematics Education Seminar
for part of my time at Auburn University.
I believe that education can be used to empower underrepresented groups,
and to that end I am committed to following best practices,
using teaching styles that help all students to learn more effectively.
I practice a modified flipped-classroom as well as I can,
and I am interested in honing this approach and growing as a teacher.
I have taught specialized courses for preservice teachers,
and I would enjoy continuing to do so at CSUSB,
including transformational and synthetic geometry for teachers.
I also have some familiarity with the CBEST algebra content,
and would enjoy teaching targeted courses.

My research is in non-associative algebras, structure theory of Lie
algebras, and Linear and Multilinear Algebra, but my training is
broad enough to teach graduate analysis, algebra, or topology.
Moreover, as a Lie theorist, I am familiar with the elementary notions
of Algebraic and Differential Geometry, and would enjoy teaching
introductory courses in those topic at CSUSB.
I have also informally studied some of the applications
of Linear Algebra,
such as the application of matrix analysis to Markov Chains,
and the applications of principle component analysis
to machine learning.
There are many directions that Linear Algebra affords for
student research, and I would enjoy working with Master's students
and with undergraduates.
As an undergraduate in the Cal State,
research was a formative experience,
essential to my understanding that knowledge
is not merely something to acquire
but rather something to actively and continually strive towards.
I feel it is essential to cultivate that understanding in our students.

Thank you for the opportunity to apply to Cal State San Bernardino
and for considering my application.
As an Inland Empire native,
I sincerely hope to join you and the rest of the CSUSB faculty
in September.

\vfill

Respectfully,

\vfill

Daniel Brice\\
\texttt{danielbrice@gmail.com}

\label{page:last}
\end{document}
