% brice-research_statement.tex %
\documentclass[11pt]{article}

\input{preamble}

\begin{document}

\makeletterhead{Research Statement}

\begin{center}
\huge Research Statement
\end{center}

\vfill

My dissertation research falls primarily into the categories of linear algebra, matrix theory, and non-associative algebras. Specifically, I studied derivations of parabolic Lie algebras and zero product determined algebras. Prior to writing my dissertation, I co-authored a paper with my advisor, Dr. Huajun Huang, on zero product determined algebras \cite{brice2015zero}.


\sechead{Zero product determined algebras}

An \emph{algebra} is a vector space $A$ equipped with a bilinear multiplication operation $\ast$. A bilinear map $\varphi : A \times A \to V$ (where $V$ is an arbitrary vector space) is said to have the \emph{zero product property} if
$$\forall x, y \in A;\quad x \ast y = 0 \text{ implies } \varphi(x,y) = 0.$$
$A$ is said to be \emph{zero product determined} if for every $\varphi$ that satisfies the zero product property, there is a linear map $f : A \to V$ such that
$$\forall x, y \in A;\quad \varphi(x,y) = f(x \ast y).$$

Motivated by applications to analysis on Banach algebras, the definition of zero product determined originated in a 2009 paper of Bre\v{s}ar, Gra\v{s}i\v{c}, and S\'{a}nches Ortega \cite{brevsar2009zero}. The authors went on to show that the algebra of $n \times n$ matrices over a field is zero product determined with respect to the usual matrix product $XY$, with respect to the Jordan product $X \circ Y = XY + YX$, and with respect to the Lie product $[X,Y] = XY - YX$. \footnote{For brevity, I restrict the above discussion to vector spaces over fields. The authors in \cite{brevsar2009zero} actually prove a more general result, showing that the matrix algebra over a unital ring $B$ over a commutative unital ring $C$ is (relative to $C$-linearity) zero product determined with respect to usual matrix multiplication and the Jordan product, and is ($C$-linear) zero product determined with respect to the Lie bracket whenever $B$ is ($C$-linear) zero product determined with respect to the Lie bracket.} Since the initial work, most research in the field has been in the direction of classifying zero product determined algebras, with contributions from Gra\v{s}i\v{c} \cite{gravsivc2010zero} and from Wang with Yu and Chen \cite{wang2011class}.

My advisor and I contributed, somewhat orthogonally, to this body of work by examining constructions on algebras that yield zero product determined algebras \cite{brice2015zero}. To achieve this, we cast the multiplication map $\ast$ as a linear map $\mu : A \otimes A \to A$. We then proved the following result:
$$(A, \mu) \text{ is zero product determined if and only if the kernel of $\mu$ is generated by rank-one tensors.}$$
Taking advantage of this new setting, we were able to prove that the direct sum of an arbitrary number of algebras is zero product determined if and only if each component algebra is zero product determined, that the tensor product of two zero product determined algebras is zero product determined,\footnote{Again, we restrict the discussion to considering vector spaces over fields, but a more general result is in fact derived.} and various conditions under which homomorphic images of a zero product determined algebra are zero product determined. We then defined a class of matrix algebras that generalize block upper triangular matrices that we call \emph{block upper triangular ladder matrix algebras}, and we showed that these matrix algebras are zero product determined with respect to the usual matrix product.

Wang, et. al. in \cite{wang2011class} showed that the parabolic subalgebras of simple Lie algebras over $\C$ are zero product determined.\footnote{Actually, over any algebraically-closed, characteristic-zero field.} In my dissertation, I use results of our prior work in \cite{brice2015zero} combined with my results on derivations (discussed below) to extend the results of Wang, et. al. to parabolic subalgebras of reductive Lie algebras over $\C$ and to the derivation algebras of such parabolic subalgebras. I am currently preparing these results for publication \cite{brice0000note}. Beyond that, I hope to determine whether or not the block upper triangular ladder matrix algebras are zero product determined with respect to the Jordan product and the Lie bracket.


\sechead{Derivations of parabolic Lie algebras}

A \emph{Lie algebra} consists of a vector space $L$ and a bilinear multiplication $[\cdot,\cdot]: L \times L \to L$ that satisfies
\begin{itemize}
	\item[] $\forall x \in L;\quad [x,x] = 0$, and
	\item[] $\forall x,y,z \in L;\quad \big[x,[y,z]\big]+\big[y,[z,x]\big]+\big[z,[x,y]\big]=0$.
\end{itemize}
A \emph{derivation} on $L$ is a linear map $d: L \to L$ that satisfies
$$\forall x,y \in L;\quad d\big([x,y]\big) = \big[d(x),y\big] + \big[x,d(y)\big]\text{.}$$

The study of derivations is motivated by connections to cohomology and the extension problem \cite{farnsteiner1988derivations}. From the definition of Lie algebra, it may be verified that for each $x \in L$ the map $y \mapsto [x,y]$ is a derivation on $L$. We call this map $\ad x$, and we call any such $\ad x$ for $x \in L$ an \emph{inner derivation}. All other derivations are termed \emph{outer.} Characterization of inner derivations is complete as part of the classical theory of Lie algebras: where $Z(L)$ denotes the center of $L$, it is well known that $\ad L \cong L / Z(L)$ \cite{humphreys1972introduction}. Characterization of outer derivations of an arbitrary Lie algebra remains an open problem. A significant portion of my dissertation research was to characterize outer derivations of parabolic subalgebras of reductive Lie algebras over both $\R$ and $\C$.

Parabolic subalgebras of Lie algebras generalize block upper triangular matrices, and their study takes a central role in the theory of Lie algebras due to their connection to representations of $L$ \cite{knapp2002lie}. In 1972, it was shown by Leger and Luks \cite{leger1972cohomology}, and independently by Tolpygo \cite{tolpygo1972cohomologies}, that all derivations of a parabolic subalgebra of a semisimple Lie algebra $L$ are inner. My dissertation extends these results by considering the case where $L$ is reductive rather than semisimple.

Let $P$ be a parabolic subalgebra of a reductive Lie algebra $L$. Let $\mathcal D$ denote the Lie algebra of derivations on $P$. We show that $\mathcal D$ decomposes as the direct sum of ideals
$$\mathcal D = \mathcal L \oplus \ad P $$
where $\mathcal L$ consists of all liner maps $d: P \to P$ that map into $Z(P)$ and map $[P,P]$ to $0$.

Concretely, we explicitly decompose $P$ as a direct sum of subspaces
$$P = Z(P) \oplus C \oplus [P,P].$$
Then $\mathcal L$ takes the form
$$\mathcal L \cong \Hom(Z(P) + C,Z(P)).$$

Using these results, we were able to accomplish our original goal of showing that $\mathcal D$ is zero product determined; however, as the problem is interesting in its own right, I am currently preparing these results for publication \cite{brice2015derivations}.

\sechead{Other potential research directions}

While my dissertation was primarily pure Mathematics, I believe I could be a valuable asset to a group doing research in applied Mathematics or in Mathematics education.

Education has always been an interest of mine. In both my undergraduate and graduate studies, I've taken research-based coursework in Mathematics eduction. In one course I designed (though never carried out) a case study dealing with the effects of calculator use on Pre-Calculus students' grasp of the graphs of the sine and cosine functions and their transformations. If given the opportunity to pursue Mathematics education, I would enjoy research into the effects of (print and software) games on the development of mathematical reasoning and into software as a means of feedback.

In many ways, linear algebra acts as the interface between pure and applied Mathematics. Problems in fields as varied as probability, graph theory, and differential equations are often reduced to questions of matrix theory, making linear algebra a valuable tool to any research team. My own interests in applied mathematics would mainly be in the intersection of linear and multilinear algebra and computer science, such as the application of multilinear tensor algorithms in web search or data analysis, or in the use of analog processors in algorithmically solving computational problems---such as inversion or the extraction of eigenvalues---in matrix theory

\sechead{References}
\printbibliography[heading=none]

\label{page:last}
\end{document}
