\documentclass[11pt]{article}

\input{../preamble.tex}

\begin{document}

\makeletterhead

\vfill

\today

\vfill

Prep Year Math Program Search Committee\\
c/o Dr. Abderrahim Elghanmi\\
Department of Mathematics and Statistics\\
King Fahd University of Petroleum \& Minerals

\vfill

To the members of the Prep Year Math Program Search Committee:

\vfill

I am contacting you today to apply for the instructional faculty
position with the Preparatory Year Math Program, Job Reference Number
F067.
I earned my PhD from Auburn University, under the direction of Huajun
Huang, in June 2014.
I spent the 2014-2015 academic year teaching at the historic Tuskegee
University, and I am currently serving as a lecturer at California
State University, Bakersfield for the 2015-2016 academic year.
Throughout my career, I have taught the full spectrum of Mathematics
courses, including College Algebra, Precalculus, and Trigonometry
courses.

To specifically address the qualifications as described in the job
listing, I am a devoted educator who approaches his teaching duties
with utmost professionalism.
I believe that the students, at every level of course, deserve as much.
I have experience working with the type of student who are likely to
be enrolled in the Prep Year Math Program, and I have to a large degree
of success worked with such students towards developing Mathematical
proficiency to a level that many of them had previously thought
unattainable.
In particular, I enjoy working with the student who sees himself as
``not a Math person,'' and I challenge him to see himself in a
different light.
I challenge all of my students to see that Mathematics, at its core,
makes sense.
I make it my goal to guide my students towards the level of maturity
to where they understand the logic of Mathematics enough to catch their
own mistakes, which I see as the chief indicator of readiness for more
advanced studies.

I have worked with online systems, such at MyMathLab, and I am not shy
around computers.
In fact I code occasionally, and I am interested in
the development and deployment of software tools that aid in the
teaching of Mathematics.
I believe that such tools, when used
appropriately, can increase access to a wider audience while honing
skills.
I enjoy working in a team towards a common goal, and I look
forward to working with the current faculty, leveraging my skills and
experience, to maintain and improve the Prep Year Math Program at KFUPM.

My continuing research interests are in matrix theory, linear algebra,
structure theory of Lie algebras, and general algebras, and I hope to
employing the resources that will be available to me at
KFUPM in furthering my research efforts, although my first priority
will of course be my teaching and administrative duties.

Thank you for the opportunity to apply to KFUPM. I sincerely hope to
hear from you soon.

\vfill

Respectfully,

\vfill

Daniel Brice\\
\texttt{danielbrice@gmail.com}

\label{page:last}
\end{document}
