\documentclass[10pt]{article}

\input{../preamble.tex}

\begin{document}

\makeletterhead

\today

The Mathematics Search Committee,\\
c/o Ms. Susan Foye,\\
Department of Mathematics,\\
California State University, East Bay

To the members of the Mathematics Search Committee:

I am contacting you today to apply for the position advertised on MathJobs.org
and on the advice of Dr. Ivona Grzegorczyk, Chair of Mathematics at Cal State Channel Islands
and Dr. Sophia Raczkowski, Chair of Mathematics at Cal State Bakersfield.
I finished my PhD at Auburn University under the direction of Huajun Huang in June 2014.
For the 2014-2015 year I served as a faculty member of Tuskegee University.
I left Tuskegee because to move closer to my family, all of whom live in California,
and I have enjoyed serving as a lecturer at Cal State Bakersfield since September.

I have been teaching Mathematics for eight years and tutoring Mathematics for over ten,
and I have had numerous experience in developmental Mathematics and Mathematics education.
During this time, I have had the opportunity to work with students from a variety of
socio-economic and ethnic backgrounds.
Having worked with a largely Hispanic student body at Ventura College and Cal State Channel
Islands and a largely African-American student body at Tuskegee University,
I am committed to increasing access for underrepresented groups.
I hope to continue this work at Cal State East Bay.

I believe that education is a social imperative:
it is for everyone, and the experience should not be dehumanizing but affirming;
it should respect the autonomy and agency of the individual.
I am committed to exercising the best practices in teaching Mathematics,
and I see incorporating technology and undergraduate research as crucial steps in improving access
and learning outcomes.
I believe that undergraduate research in particular creates the sense of agency for the student
and provides for more student-teacher interaction.

I can teach any undergraduate Mathematics course, including the specialized courses for
pre-service teachers.
I have taught such courses in the past, and enjoy the opportunity to broaden the students' horizons
by exploring the concrete realizations of the highly abstract concepts.
I can further teach graduate courses in Analysis, Topology, and Algebra.

My research interests are in linear and multilinear algebra and in the structure theory of Lie algebras.
Linear algebra provides a concrete interface to more abstract fields of algebra, and thus lends itself
well to undergraduate and masters-level research. I would very much enjoy continuing my research and mentoring
undergraduates and masters students in Hayward, even to the point of ferrying students to and from conferences.
I found the interactions I had with my professors through undergraduate research particularly rewarding,
and I will love the opportunity to provide the same experience to my future students.

Thank you for this opportunity to apply for the faculty position at Cal State East Bay and for
considering my application. I sincerely hope to serve with you in Hayward the coming Fall.

Respectfully,
\vfill
Daniel Brice\\
\texttt{danielbrice@gmail.com}

\label{page:last}
\end{document}
