\documentclass[11pt]{article}

\input{../preamble}

\begin{document}

\makeletterhead{Cover Letter}

\today

Developmental Mathematics Coordinator Search Committee,\\
c/o Dr. Serban Raianu\\
Department of Mathematics\\
California State University, Dominguez Hills

To the Developmental Mathematics Coordinator Search Committee:

I am contacting you today to apply for the position advertised on MathJobs.org
and on the advice of Dr. Ivona Grzegorczyk, Chair of Mathematics at Cal State Channel Islands.
I finished my PhD at Auburn University under the direction of Huajun Huang in June 2014,
and for the 2014-2015 year I have been serving as a faculty member of Tuskegee University.
I am leaving Tuskegee because I am moving to Southern California for family reasons.

I have been teaching Mathematics for eight years and tutoring Mathematics for over ten,
and I have had numerous experience in developmental Mathematics and Mathematics education.
During this time, I have had the opportunity to work with students from a variety of
socio-economic and ethnic backgrounds.
Having worked with a largely Hispanic student body at Ventura College and Cal State Channel
Islands and a largely African-American student body at Tuskegee University,
I am committed to opening doors for underrepresented groups.
I hope to continue this work at Cal State Dominguez Hills.

I believe that education is a social imperative:
it is for everyone, and the experience should not be dehumanizing but affirming;
it should respect the autonomy and agency of the individual.
I am committed to exercising the best practices in Mathematics education,
and I see incorporating technology in this way as a next step in that process.
I am excited about the prospect of incorporating technology into the developmental Mathematics
program at Dominguez Hills,
particularly in finding ways to move the presentation aspect of the courses to a self-paced
format and the practice aspect to the classroom.
I believe that this approach helps restore the sense of agency to the student
and provides for more student-teacher interaction.

I have some experience coding web applications, and I am a quick study.
I will be more than capable of administering the online systems used in the developmental
Mathematics program.
I am also excited about the management side of the position.
I enjoy working with people, and I have had many opportunities to effectively manage groups
outside of my academic and professional life,
such as through Scouting, various Puzzle-hunt events, and STEMS outreach events at Auburn.

Thank you for this opportunity to apply for Developmental Mathematics Coordinator and for
considering my application. I sincerely hope to serve with you at Dominguez Hills this Fall.

Respectfully,
\vfill
Daniel Brice\\
\texttt{danielbrice@gmail.com}

\label{page:last}
\end{document}
