\documentclass[11pt]{article}

\input{../preamble.tex}

\begin{document}

\makeletterhead

\vfill

\today

\vfill

The VAP Search Committee,\\
c/o Dr. Dagan Karp,\\
Department of Mathematics,\\
Harvey Mudd College,\\
Claremont, CA

\vfill

To the members of the VAP Search Committee:

First, thank you for taking the time to consider my application. I am
contacting you today to apply for the Visiting Assistant Professor
position advertised on MathJobs.Org. My name is Daniel Brice, and I
completed my PhD at Auburn University, under the direction of Huajun
Huang, in August 2014. Since then, I spent one year serving as an
Assistant Professor at the renowned Tuskegee University and one year
serving as a Lecturer at California State University, Bakersfield.

My research interests are in structure theory of Lie algebras, linear
and multilinear algebra, and zero-product determined algebras. My papers
appear in \emph{Linear and Multilinear Algebra} and in the \emph{Alabama
Journal of Mathematics}. Despite my full-time teaching load at CSUB, I
managed to author one paper and submit one paper, and I am currently
working on two projects, one at the typesetting stage and one at the
research stage. Please see my included Research Statement and Curriculum
Vitae for details.

I believe that you will find that I am more than a satisfactory teacher.
I have had the honor of working with underrepresented groups at Tuskegee
and CSUB, and I am committed to continuing to provide access for
underrepresented groups in my future teaching and mentoring duties.
I am able to teach any undergraduate course, including coding-heavy
courses, as I am familiar with Haskell, Java, and Python. Moreover,
linear algebra lends itself to undergraduate research in the sense that
many problems I approach will, after several layers of transformation,
eventually boil down to linear algebra, making high-level Mathematics
accessible to the undergraduate researcher. As such, I believe that I
would make a valuable contribution to the undergraduate research at
Harvey Mudd.

Again, thank you for considering my application. I look forward to
hearing from the search committee, and I look forward to joining you
in Claremont this coming Fall.

\vfill

Respectfully,\\

Daniel Brice\\
\texttt{danielbrice@gmail.com}

\label{page:last}
\end{document}
