\documentclass[11pt]{article}

\input{../preamble.tex}

\begin{document}

\makeletterhead{}

\vfill

\today

\vfill

RTG in Algebra, Algebraic Geometry, and Number Theory,\\
c/o Dr. Elham Zelmanov,\\
Department of Mathematics,\\
University of California, San Diego

\vfill

To the (Co-)Principal Investigators of the RTG in Algebra, Algebraic
Geometry, and Number Theory:

\vfill

My name is Daniel Brice, I am currently a Lecturer in the Department of
Mathematics at California State University, Bakersfield, and while I
enjoy my work, I am pursuing a more research-oriented career. I am
writing you today to apply for the postdoc position in the RTG in
Algebra, Algebraic Geometry, and Number Theory.

I complete my PhD in June 2014 under the direction of Huajun Huang at
Auburn University, Alabama. My dissertation involved classifying the
derivations of parabolic subalgebras of reductive Lie algebras. I
arrived at a direct sum decomposition of the derivation algebra, which I
used to show that the derivation algebra is zero product determined (a
recent notion that is related to the linear preserver problem of
operator theory).

As a member of the RTG at UC San Diego, I would be interested in
extending my results to prime characteristic, for which I may seek Dr.
Kedlaya's advice. I would also be interested in working with Dr.
Zelmanov on zero product determined Jordan algebras, which is becoming
an active area of research. Apart from those specifics, I am largely
amicable to the direction of research that the RTG sees fit,
particularly as I would like to explore more algebraic geometry. I am
ambitions, resourceful, and enjoy working in a team towards a common
goal (one of the things I sorely miss in my current teaching position).
I am a frequent expositor: I enjoy attending and presenting in
colloquia, and I enjoy working with students. I am also a hobbyist
Haskell coder and am familiar with Maple. I am exited about the prospect
of learning how to leverage more advanced tools, such as SAGE and GAP,
in my research.

With this cover letter, I have included reference letters from my
dissertation advisor Huajun Huang, and from Dr. T. Y. Tam, Chair of
Mathematics at Auburn University (who served on my PhD committee), and
Dr. Ivona Grzegorczyk, Chair of Mathematics at Cal State Channel
Islands. Also included are my Curriculum Vitae, Research Statement,
Teaching Statement, Publication List, and Personal Statement on
Contributions to Diversity. Thank you for the opportunity to apply and
for considering my application. I sincerely hope to join you in La Jolla
this summer.

\vfill

Respectfully yours,

\vfill

Daniel Brice\\
\texttt{danielbrice@gmail.com}

\label{page:last}
\end{document}
