\documentclass[11pt]{article}

\input{../preamble.tex}

\begin{document}

\makeletterhead

\vfill

\today

\vfill

Hiring Committee\\
c/o Dr. Rabia Djellouli\\
Department of Mathematics\\
California State University, Northridge

\vfill

To the members of the Hiring Committee:

\vfill

I am contacting you today, on the advice of Ivona Grzegorczyk, Chair of
Mathematics at Cal State Channel Islands and Sophia Raczkowski, Chair of
Mathematics at Cal State Bakersfield, to apply for the Assistant
Professorship in Algebra, joblist-1501-8135 on MathJobs.org. I completed
my PhD under the direction of Huajun Huang at Auburn University in June
2014. I am currently a lecturer at Cal State Bakersfield, and while I
enjoy my teaching responsibilities, I am seeking a permanent position
that incorporates research and service responsibilities.

I have been teaching college Mathematics since 2007, starting as an
undergraduate assistant at Cal State Channel Islands. In that time, I
have had the opportunity to teach a diverse student body across the
curriculum, including developmental Mathematics and courses targeted at
preservice teachers and CSET preparation. I enjoy teaching these
courses, and would enjoy the opportunity to teach graduate courses in
algebra, geometry, topology, and analysis at CSUN.

My research is in Lie algebras, linear algebra, and matrix theory, and I
have dabbled in applications to computer vision and data analysis. I
have several directions for my future research in mind, and I would like
to work with students to pursue those avenues. I would also be
interested in seeing what Drs. Neubauer, Sethuraman, and Stevenson are
working on, in case it is something with which I might be able to
assist.

I am particularly interested in CSUN because I love the valley, and I am
energized by large, cosmopolitan campuses. I see that CSUN supports an
ongoing Algebra/Number Theory/Discrete seminar that I am interested in
supporting. I am also interested in supervising undergraduate and
graduate research, and organizing logistics and funding for conference
trips for the students. I believe strongly that students need a sense of
agency, which is perhaps best nurtured through student research. I am
also interested in the service opportunities that being in a major
metropolitan area affords, such as helping Dr. Fernandez with AMC, or
even organizing CSUN Mathematics Puzzle Events, akin to those I've help
with at Auburn.

Included with this cover letter are my curriculum vitae, three letters
of reference---from Ivona Grzegorczyk, from my advisor
Huajun Huang, and from Chair of Mathematics and Statistics at Auburn
T.Y. Tam---my research statement, and my teaching statement. Thank you
for considering my application. I sincerely hope to serve with you in
Northridge this August.

\vfill

Respectfully,

\vfill

Daniel Brice\\
\texttt{danielbrice@gmail.com}

\label{page:last}
\end{document}
