\documentclass[11pt]{article}

\input{../preamble.tex}

\begin{document}

\makeletterhead

\vfill

\today

\vfill

Search Committee\\
c/o Dr. David Zeigler\\
Department of Mathematics and Statistics\\
California State University, Sacramento

\vfill

To the members of the Search Committee:

\vfill

I am contacting you today on the advice of Ivona Grzegorczyk, Chair of Mathematics at Cal State Channel Islands, and Sophia Raczkowski, Chair of Mathematics at Cal State Bakersfield, to apply for the Assistant Professor position, joblist-969-8219 on MathJobs.org, at Cal State Sacramento.
I completed my PhD in June 2014 at Auburn University under the direction of Huajun Huang. 
I am currently lecturing at Cal State Bakersfield, and while I am happy with my current teaching duties, I am seeking a position which includes research and service duties.

I have had the honor of serving a diverse body of students across the curriculum, at two Cal States (Channel Islands and Bakersfield), Auburn University, and the historic Tuskegee University, since 2007.
I have experience teaching developmental Mathematics, the Calculus sequence, and courses catering to preservice teachers.
I am familiar with the topics covered on the CSET and would enjoy teaching CSET preparatory courses.
My preliminary exams where in Algebra, Analysis, and Topology, and I have experience assisting and grading both Algebra and Analysis and am able to teach any of those three, and the various geometries, to advanced undergraduates and graduate students.
I practice a blend of Socratic methods and the flipped classroom, drawing inspiration from the best practices of inquiry-based learning, incorporating technology into activities with a view towards applications where appropriate.
Please see my attached Teaching Statement for more details.

My research interests are primarily in structure theory of Lie algebras, though my training is varied and includes matrix theory, applications of linear algebra to computer vision and data analysis, representation theory, homological algebra, commutative algebra, and group theory.
I am currently investigating structural decompositions of a generalization of block upper triangular matrix algebras and how these algebras relate to the zero-product preserver problem of Operator Theory.
These problems often reduce to linear algebra, making them suitable for undergraduate and master's research, and I would enjoy working with students on these topics, as I believe that research is an integral part of active learning.
I fondly remember traveling to conferences with my professors during my undergraduate at Cal State Channel Islands, and I would embrace the chance to afford my students at Cal State Sacramento the same opportunities by seeking external funding and organizing trips.

Thank you for this opportunity to apply. I sincerely hope to join the Cal State Sacramento faculty this coming Fall.

\vfill

Respectfully,\\
Daniel Brice\\
\texttt{danielbrice@gmail.com}

\label{page:last}
\end{document}
