\documentclass[11pt]{article}

\input{../preamble.tex}

\begin{document}

\makeletterhead{}

\vfill

\today

\vfill

Department of Mathematics\\
c/o Dr. Charles Lam, Chair, Search Committee\\
School of Natural Sciences, Mathematics, and Engineering\\
California State University, Bakersfield

\vfill

To the members of the Mathematics Search Committee:

\vfill

I am contacting you today on the recommendation of Dr. Sophia Raczkowski
to apply for the tenure-track position advertised on MathJob.Org. I
earned my PhD from Auburn University in June 2014 under the direction of
Huajun Huang, authoring my dissertation titled ``On the derivation
algebras of reductive Lie algebras with applications to zero product
determined algebras.'' Since completing my doctorate, I spent one year
as an Assistant Professor at the historic Tuskegee University and later
accepted a Lecturer position at CSU Bakersfield in order to relocate for
family reasons.

Since completing my doctorate, my publications have appeared in
\emph{Linear and Multilinear Algebra} and the \emph{Alabama Journal of
Mathematics}, both representative of research independent of my
dissertation research. While at CSU Bakersfield, I codified my
dissertation research into two papers, one of which has been submitted
and one of which is still being refined. My research has been in
structure theory of Lie algebras and in zero product determined
algebras, and it interfaces strongly with applied disciplines such as
Linear algebra, tensor decomposition, and operator theory. I'm
interested in the prospect of expanding the scope of my research, and
I'm excited about the idea of working in an interdisciplinary team at
CSUB. I am currently meeting regularly with Chris Mike to discuss Lie
groups, and several other students have approached me to inquire about
student research. I look forward to continuing to work with Chris and
with working with my other students.

I can code in Haskell, Java, Javascript, and Python, and I am familiar
with the principles of both object-oriented programming and functional
programming. I would be happy to leverage this expertise by teaching
computation-heavy Mathematics courses such as Numerical Analysis and
Data Science, or towards developing a numerical/computational approach
to the Calculus sequence.

Finally, my teaching record is impeccable. Please see my department
review, my SOCIs, and my RateMyProfessors.com reviews (low Easiness,
high Clarity, high Helpfulness) for verification of this claim. I am
able to teach any undergraduate course with only a minimum of direction
from the coordinator, and I am interested in supervising student
assistants and peer tutors as the need arises.

\vfill

Respectfully,

\vfill

Daniel Brice\\
\texttt{danielbrice@gmail.com}

\label{page:last}
\end{document}
