\documentclass[11pt]{article}

\input{../preamble.tex}

\begin{document}

\makeletterhead

\vfill

\today

\vfill

VAP Search Committee,\\
Department of Mathematics,\\
University of California, Santa Barbara

\vfill

To the VAP Search Committee:

\vfill

My name is Daniel Brice, and I am currently a Lecturer in the Department
of Mathematics at California State University, Bakersfield. While I
enjoy my work, I am pursuing a more research-oriented career. I am
writing you today to apply for the Visiting Assistant Professor position
advertized on MathJobs.Org.

I complete my PhD in June 2014 under the direction of Huajun Huang at
Auburn University, Alabama. My dissertation involved classifying the
derivations of parabolic subalgebras of reductive Lie algebras. I
arrived at a direct sum decomposition of the derivation algebra, which I
used to show that the derivation algebra is zero product determined (a
recent notion that is related to the linear preserver problem of
operator theory).
As my work is largely motivated by the linear preserver problem,
admitting applications to functional analysis, I would be interested in
working with Dr. Akemann and Dr. Goodearl in exploring the connections
between my work and linear operators. I'm also interested in extending
my results to the prime characteristic case, in which case I would seek
to work with Dr. Jacob.

Having grown up in, studied in, and taught in California, I
understand the dynamics of teaching to a diverse student body. In my
teaching, I demonstrate my committment to diversity, equity, and
inclusion by practicing a variant of the flipped-classroom model. I have
high expectations of all of my students, and I give them meaningful and
timeley feedback. In my service, I have contributed to equity by
volunteering my time in public schools in Oxnard, CA, bringing age
appropriate problems in graph theory to middle-school students, and by
assisting with the running of outreach events such as Science Olympiad
and AMP'd Challenge, bringing contemporary Mathematics to middle- and
high-school-aged students of a variety of socio-economic backgrounds.

With this cover letter, I have included reference letters from my
dissertation advisor Huajun Huang and from Dr. T. Y. Tam, Chair of
Mathematics at Auburn University (who served on my PhD committee), and
Dr. Ivona Grzegorczyk, Chair of Mathematics at Cal State Channel
Islands. Also included are my Curriculum Vitae, Research Statement,
Teaching Statement, and Publication List. Thank you for the opportunity
to apply and for considering my application. I sincerely hope to join
you in Goleta this July.

\vfill

Respectfully yours,

\vfill

Daniel Brice\\
\texttt{danielbrice@gmail.com}

\label{page:last}
\end{document}
